working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-11 Manuscript_draft/Manuscript_draft.Rmd
Some edits in results Markdown

Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did, out of nine. The treatments of 100% heterospecific pollen were all significantly different from the cross except one, *Sinapis alba* with pollen from another Brassicaceae, *Brassica oleracea*. Just few treatments of 100% pollen produced seeds... A summary of the results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in table 2.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("table_treatments.RData")

table<- data.frame(cross, self, nat_self,apo)
kable(table, format="markdown")
```

>>>>

Results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in table 2. Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine. The 100% foreign pollen treatments barely produced seeds or fruits and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial. Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases. *S. lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size. *C. annum* produced some fruits (9%) of both small and normal size and finally *S. melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of no production of fruit in apomictic treatments.

**Table 2**. Perecentage of seeds produced per ovule for the ten species used in the experiment. The treatments presented are hand cross pollination, hand self pollination, natural selfing and apomixis (emasculated flowers).
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("table_treatments.RData")
Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
Cross <- cross
Self <- self
Natural_selfing <- nat_self
Apomixis <- apo
table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
kable(table, format="markdown")
```

### 2018-12-11 Manuscript_draft/Manuscript_draft.tex
Table transferred to Markdown
Some edits in results Markdown

Heterospecific pollen reduced seet set signifcatively with the 50-50\%
heterospecific pollen treatments for 65\% of the pairwise interactions
p\textless{}0.05. Across families we found a very similar effect but
when species where look at species level they respond differently even
within the same family, for instance for two species of the Brassicaceae
family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
very contrasting effects of foreign pollen where for the first one, all
donors reduce seed set significatively and for the second, just two
species did, out of nine. The treatments of 100\% heterospecific pollen
were all significantly different from the cross except one,
\emph{Sinapis alba} with pollen from another Brassicaceae,
\emph{Brassica oleracea}. Just few treatments of 100\% pollen produced
seeds\ldots{} A summary of the results of hand cross pollination, self
hand pollination, natural selfing and apomixis are presented in table 2.

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}

>>>>

Results of hand cross pollination, self hand pollination, natural
selfing and apomixis are presented in table 2. Heterospecific pollen
reduced seet set signifcatively with the 50-50\% heterospecific pollen
treatments for 65\% of the pairwise interactions p\textless{}0.05.
Across families we found a very similar effect but when species where
look at species level they respond differently even within the same
family, for instance for two species of the Brassicaceae family
\emph{Brassica oleracea} and \emph{Eruca versicaria} we found very
contrasting effects of foreign pollen where for the first one, all
donors reduce seed set significatively and for the second, just two
species did out of nine. The 100\% foreign pollen treatments barely
produced seeds or fruits and just for \emph{Sinapis alba} we did not
find significant differences between the hand cross pollination and one
treatment with pollen from a confamilial. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases.
\emph{S. lycopersicum} seems to produced small fruits (35\% of the
treatments) independently of pollen and pollen donor due to also
apomictic treatments did, never normal size. \emph{C. annum} produced
some fruits (9\%) of both small and normal size and finally \emph{S.
melongena} produced seedless normal fruits with just confamilial pollen
(3\%), for both species seems that fruit formation was induced by pollen
on the stigma because of no production of fruit in apomictic treatments.

\textbf{Table 2}. Perecentage of seeds produced per ovule for the ten
species used in the experiment. The treatments presented are hand cross
pollination, hand self pollination, natural selfing and apomixis
(emasculated flowers).

\begin{longtable}[]{@{}lrrrr@{}}
\toprule
Species & Cross & Self & Natural\_selfing & Apomixis\tabularnewline
\midrule
\endhead
Brassica oleracea & 32.06897 & 0.0000000 & 0.00000 & 0\tabularnewline
Brassica rapa & 44.97041 & 0.0000000 & 0.00000 & 0\tabularnewline
Eruca versicaria & 23.75000 & 0.4166667 & 0.00000 & 0\tabularnewline
Sinapis alba & 43.33333 & 48.3333333 & 5.00000 & 15\tabularnewline
Ipomoea aquatica & 40.00000 & 30.0000000 & 20.00000 & 0\tabularnewline
Ipomoea purpurea & 31.66667 & 86.6666667 & 31.66667 & 0\tabularnewline
Capsicum annuum & 100.00000 & 66.2240664 & 23.48548 & 0\tabularnewline
Petunia integrifolia & 100.00000 & 24.7727273 & 0.00000 &
0\tabularnewline
Solanum lycopersicum & 90.38043 & 43.4782609 & 70.00000 &
0\tabularnewline
Solanum melongena & 60.47525 & 87.9702970 & 21.56436 & 0\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}
